### 2010-03-15 papers/icfp-2010-desc/paper_type_theory.tex
IDesc@ICFP: clarify elaboration/distillation

The abstraction we have developed in this section are entirely
transparent to the user. In the case of finite function space, the
user has never to explicitly \emph{call} the $\F{switch}$
eliminator. Nor will she \emph{be presented} the elaborated term, only
the high-level one. Bidirectional type-checking and type-directed
pretty-printing seal the low-level type theory behind the high-level
expressions.

\note{And suddenly, type-directed pretty printing comes into the
  picture. Surely, it should ``just'' be the inverse of
  elaboration. But is it? And how do we present it?}

>>>>

The abstraction we have developed in this section are entirely
transparent to the user. In the case of finite function space, the
user has never to explicitly \emph{call} the $\F{switch}$
eliminator. For diagnosis purposes, a similar, reverse mechanism turns
low-level terms into high-level expressions. Hence, this system, which
presentation is out of the scope of this paper, seals the low-level
type theory behind the high-level expressions.
